
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Milan Ramdhari} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1 650-307-3592 ~ \href{mailto:milanramdhari45@vt.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{milanramdhari45@vt.edu}} ~ 
    \href{https://linkedin.com/in/milanramdhari/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/milanramdhari}}  ~
    % \href{https://github.com/milanramdhari}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/milanramdhari}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Virginia Polytechnic Institute and State University (Virginia Tech)}{August 2022 -- May 2026}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{Blacksburg, VA}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    \small
    Data Structures and Algorithms, Machine Learning, Software Design, Computer Vision, Deep Learning, Computer Organization, Computer Systems, Applied Combinatorics, Statistics, Linear Algebra, Discrete Math


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineering Intern}{June 2025 -- November 2025}
      {Viven.ai}{Santa Clara, CA}
      \resumeItemListStart
        \resumeItem{Engineered backend services for a conversational AI knowledge bot using Python, Next.js, TypeScript, React, DynamoDB, S3, gRPC, and Redis.}
        \resumeItem{Implemented APIs in Next.js and integrated Python Flask services for RAG queries, enabling automated email delivery of chat responses via AWS SES.}
         \resumeItem{Developed scheduling workflows to automate timely message delivery and trigger system events, improving user engagement.}
         \resumeItem{Contributed to the development of a real-time call agent leveraging Twilio, OpenAI, and WebSockets to enable live interactive sessions.}
         \resumeItem{Automated end-to-end testing using Playwright, building the entire E2E framework from scratch and implementing 150+ fully automated test scenarios.}
      \resumeItemListEnd
      \vspace{6pt}


      \resumeSubheading
        {Undergraduate Teaching Assistant - Data Structures and Algorithms}{July 2025 -- September 2025}
        {Virginia Tech}{Blacksburg, VA}
        \resumeItemListStart
        \resumeItem{Assisted in teaching core data structures concepts, including linked lists, stacks, queues, trees, and graphs.}
        \resumeItem{Hosted weekly office hours, providing one-on-one guidance and support to over 100 students.}
        \resumeItem{Graded assignments and projects, ensuring consistent application of grading rubrics and providing constructive feedback.}
    \resumeItemListEnd
    \vspace{6pt}


    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- June 2023}
      {Trademo Inc.}{Gurugram, HR}
      \resumeItemListStart
        \resumeItem{Developed a data pipeline to ingest Mexico’s trade data into the company database.}
        \resumeItem{Gained experience in Python - used NumPy \& Pandas library.}
        \resumeItem{Helped expand Trademo Database by transforming existing trade data.}
    \resumeItemListEnd
\vspace{6pt}

    \resumeSubheading
      {Volunteer Software Developer}{ April 2022 -- June 2022}
      {Sitare Foundation}{Gurugram, HR}
      \resumeItemListStart
        \resumeItem{Collaborated in a team of 4 students to develop a note-sharing platform using HTML, Bootstrap, and PHP.}
        \resumeItem{Conducted SQL testing to ensure efficient database handling for high data loads.}
    \resumeItemListEnd
    \vspace{6pt}

    
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
  {StudentStash}{July 2024 -- August 2024}
  {}{}
\vspace{-4ex} % Adjust this value if needed
\resumeItemListStart
  \resumeItem{Co-developed StudentStash, a marketplace for college students, using React.js and Node.js.}
  \resumeItem{Optimized platform performance and enhanced user interface and core functionalities.}
  \resumeItem{Secured user passwords and sensitive information using bcrypt.js.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%

%-----------PROJECTS-----------
\section{Leadership}
\resumeSubHeadingListStart

\resumeSubheading
  {GenOne Mentor}{June 2023 -- May 2024}
  {Virginia Tech}{Blacksburg, VA}
\resumeItemListStart
  \resumeItem{Mentored 30 first-generation freshmen through one-on-one and group sessions.}
  \resumeItem{Tracked student progress and provided personalized support to promote academic success and personal development.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, TypeScript, Java, C, JavaScript, Assembly, PHP, SQL} \\
     \textbf{Frameworks}{: Flask, Next.js, React.js, Node.js, Bootstrap} \\
     \textbf{Developer Tools}{: Git, AWS SES, DynamoDB, OpenSearch, Redis, Pytest, Pylint,  MATLAB, MySQL, Playwright, CI/CD} \\
     \textbf{Libraries}{: Zod, tRPC, NumPy, Pandas, Scikit-learn} \\
    }}
 \end{itemize}


%-----------AWARDS---------------
% \section{Awards}
% \begin{itemize}[leftmargin=*]
%   \item \textbf{Sitare Foundation Scholarship}: 
%   Awarded Sitare Foundation Scholarship for free education in middle and high school. This scholarship is provided to underprivileged students demonstrating outstanding academic achievements.
% \end{itemize}

\end{document}
